Magalhaes and Schwilk Supplementary Materials

### 2019-07-24 ms/SI.tex
Solve units issue with spread rate
It turns out that one of the metadata files stored with data had
incorrect information on units. Also, the description of some variables
was incorrect. A root issue is that the actual raw data is all missing,
the data as committed by Rita already includes calculations such as
spread rate and is missing the raw flaming start and end times, etc. I
must assume those simple calculations are correct, I am sure they are,
but it would be best to have the raw data with stopwatch times.

\begin{table}[h]
  \caption{Mixed model coefficients for flame spread rate. Table shows mixed linear model results  TODO.} 
  \label{tabS3}
\centering
\input{figs_tables/spreadrate-coef-tab.ltx}
\end{table}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=8cm]{figs_tables/SI_fig1_drydown_curves_logged.pdf}
   \label{SI_fig1}
\caption[Semi-log scale dry down curves for eight litter types.]{Lines show best-fit lines fit to the natural log of moisture content on a dry mass basis.  The slope of the line shows the dessication rate ($hr^{-1}$). Litter samples we saturated by immersion for 24 hours and then allowed to drain by gravity for 3 min before initial weighing. Colors indicate genera and there were significant differences in both }

>>>>

\begin{table}[h]
  \caption{Mixed model coefficients for flame spread rate. Table shows mixed linear model results.} 
  \label{tabS3}
\centering
\input{figs_tables/SI_tab2_spread_moist_coef.ltx}
\end{table}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=8cm]{figs_tables/SI_fig1_drydown-curves_logged.pdf}
   \label{SI_fig1}
\caption[Semi-log scale dry down curves for eight litter types.]{Lines show best-fit lines fit to the natural log of moisture content on a dry mass basis.  The slope of the line shows the dessication rate ($hr^{-1}$). Litter samples we saturated by immersion for 24 hours and then allowed to drain by gravity for 3 min before initial weighing. Colors indicate genera and there were significant differences in both }
